\section{Estimation of the angular measure\label{sec:methodology}}

To infer the PoT distribution we consider two steps: First we 
    estimate the shape and scale parameters for the
    multivariate Pareto distribution, using the univariate marginals; Then 
    we focus on the dependence structure in extreme regions by proposing a 
    flexible model for the distribution of $\bm{V}$.  
    % Consider a collection of 
    % observations  $\bm{w}_i \in {\mathbb R}^d, i = 1, \ldots, n$ that exhibit 
    % extreme behavior.  
    Consider $\bm{w}_i,\;i =1,\ldots,n$ a collection of realizations of $\bm{W}$.
    We start by setting a large threshold 
    $b_{t,\ell}$ for the  $\ell$-th marginal, $\ell = 1, \ldots,d$. Then, the 
    distribution of $W_\ell$, conditional on exceeding the threshold, can be 
    approximated with a generalized univariate Pareto. Thus,
    \[
    \Pr[W_\ell>w_{i\ell} \mid W_\ell>b_{t,\ell} ]= \left(1 + \xi_\ell
    \frac{w_{i\ell} - b_{t,\ell}}{\sigma_\ell}\right)_+^{-1/\xi_\ell}
    \]
    where $(\cdot)_+$ indicates the positive part function.  We set 
    $b_{t,l}  = \hat{F}^{-1}_{\ell}(1 - 1/t)$, the the empirical $(1-1/t)$-quantile.  
    We then estimate $\xi_\ell$ and $\sigma_\ell$,
    for each $\ell$, using likelihood based methods. To estimate 
    the angular distribution, we standardize each of the marginals. 
    The standardization yields
    \begin{equation}
            \label{eqn:standardization}
            z_{i\ell} = \left(1 + \xi_{\ell}\frac{w_{i\ell} -
                b_{t,\ell}}{\sigma_{\ell}}\right)_{+}^{1/\xi_{\ell}}\; .
        \end{equation}
    Note that $z_{i\ell}> 1$ implies that $w_{i\ell} > b_{t,\ell}$, meaning 
    that the observation $\bm{w}_i$ is extreme in the $\ell$-th dimension. 
    Thus, $r_i = \|\bm{z}_i\|_\infty > 1$ implies that at
    least one dimension has an extreme observation, and corresponds 
    to a very extreme observation when $t$ is large. We focus on 
    the observations that are such that $r_i > 1$. These provide a
    sub-sample of the stardardized original sample. We define $\bm{v}_i = 
    \bm{z}_i /r_i \in  \mathbb{S}_{\infty}^{d-1}$. These vectors are used 
    for  the estimation of $\Phi$. 
    % We observe that in practice, the choice
    % of $\bm{b}$, and the subsequent fitting of $\bm{a}$ and $\bm{\xi}$ induces
    % a stochastic element in the spectral distribution that is not accounted for
    % in our analysis.  \makenote{phrasing?} \bruno{\bf Peter: What are you trying 
    % to say here? I would not open the can of worms of trying to do all in one
    % step, so I would delete the sentence starting with ``We observe ... ''}

\input{methodology_projgamma}

% EOF